Fractional Types

### 2019-11-20 fracGC/p.tex
before merge

The metavariable $\net$ excludes all types that are equivalent to the
empty type, e.g., $(1 + 1) * 0$. For now, all gc values are
represented at runtime using a trivial value denoted by $\gcv$. We
also explicitly add the desired coherence condition on the creation
and annihilation process as a level-2 program that would enforce the
duality of $\eta$ and $\epsilon$. At this point, an application of
$\eta$ following by $\epsilon$ might however throw an exception.

@@

@@

%%%%% 
\subsection{State of the Art}

current proposals for reversible
and quantum programming languages
(e.g. Ricercar~\cite{10.1007/978-3-319-20860-2_13},
Quipper~\cite{Green:2013:QSQ:2491956.2462177}), restrict ancilla bits
to be used in nested scopes, have sound but incomplete laws for
reasoning about the safety condition, and only guarantee safety via
runtime checks.

Ricercar quote:
\begin{quote}
  Checking that some defined ancillae are indeed unchanged for all
  possible input vectors of an arbitrary description is hard; in
  general, one has to test all possible input vectors, which is
  undesirable. For a reversible programming language such as Janus
  [22], this is therefore imple- mented as a runtime check that checks
  the reversibility of a program only in rela- tion to the executing
  input vector. This is also the case for the syntax described in
  Fig. 1.

  To be able to introduce and remove ancilla wires from a circuit, we
  have identified the need for five basic rules.
\end{quote}

>>>>

The metavariable $\net$ excludes all types that are equivalent to the
empty type, e.g., $(1 + 1) * 0$. For now, all gc processes are
represented at runtime using a trivial value denoted by $\gcv$. We
also explicitly add the desired coherence condition on the creation
and annihilation process as a level-2 program that would enforce the
duality of $\eta$ and $\epsilon$. At this point, an application of
$\eta$ following by $\epsilon$ might however throw an exception.

@@

By lifting the scoping restriction, the development in the previous
section is already more general than the state of the art in ancilla
management.  It however shares the same limitation of requiring a
runtime check to ensure ancillae values are properly restored to their
allocation~\cite{10.1007/978-3-319-20860-2_13,Green:2013:QSQ:2491956.2462177}.
In this section, we address this limitation using a combination of
pointed types, singleton types, monads, and comonads.

%%%%% 
\subsection{Lifting Evaluation to Type System}

Before giving all the (rather involved) technical details, we
highlight the main idea using the toy language below:

@@
